Compare pseqs

### 2019-05-23 comparepseqs.Rmd
save bray also

```{r rds files}
rds <- list("R16S" = "data/phfinrisk_16S_otu_raw_2019-02-19.RDs",
            "shogun" = "data/phfinrisk_species_all_drop50k_2018-12-21.RDs",
            "centrifuge" = "data/phfinrisk_centrifuge_species_all_2018-11-30.RDs",
            "gtdb" = "data/phfinrisk_gtdb_species_all_drop50k_2019-01-14.RDs",
            "ncbi" = "data/phfinrisk_custom70_species_all_2019-01-29.RDs")
```

@@

@@

@@

alphadiversity[["ncbi"]]
betadiversity[["ncbi"]]

betadiversity

ls()

a <- mergediversities(alphadiversity[["ncbi"]], betadiversity[["ncbi"]])

alphadiversity[["ncbi"]]
betadiversity[["ncbi"]]

names(betadiversity)
betadiversity[[""]]

 alpha.select <- alphadiversity[["R16S"]][["min"]] %>% select(estimate, p.value, response)

beta.rbind <- betadiversity[["R16S"]][["min"]] %>%
    data.table::rbindlist(id = "model_name")

%>%
            dplyr::filter(term %in% responses) %>%
            dplyr::select(response, R2)

        merge( alpha.select , beta.rbind, by = "response") %>%
            merge(names.dset %>% select(Covariate, Category, Name), by.x ="response", by.y = "Covariate") %>%
            mutate(Qstar = ifelse(p.value < 0.05, '*', ' '))
    })

vectortolist(names(alphadiversity[["R16S"]]))

c2l(names(pseq))
beta.min <- lapply(c2l(names(pseq)), function(x) {
    mergediversities(alphadiversity[[x]], betadiversity[[x]])
})

beta.min[[1]] %>%
         data.table::rbindlist(id = "model_name")

#            dplyr::filter(term %in% responses) %>%
            dplyr::select(response, R2)

>>>>

```{r rds files}
rds <- list("shogun" = "data/phfinrisk_species_all_drop50k_2018-12-21.RDs",
            "centrifuge" = "data/phfinrisk_centrifuge_species_all_2018-11-30.RDs",
            "gtdb" = "data/phfinrisk_gtdb_species_all_drop50k_2019-01-14.RDs",
            "ncbi" = "data/phfinrisk_custom70_species_all_2019-01-29.RDs",
            "R16S" = "data/phfinrisk_16S_otu_raw_2019-02-19.RDs")
```

@@

    saveRDS(bray.dist.matrix,
            file = paste0("rds-comparepseqs/bray-", key , ".rds"))

@@

```{r plot, eval = FALSE}
plotlist <- list()

for (key in names(rds)) {
    diversities <- mergediversities(ret[[key]][["alphadiversity"]],
                                    ret[[key]][["betadiversity"]])

    alpha.diversity.min <- plot.alpha(diversities$min, colorlimit = 0.6)
    alpha.diversity.max <- plot.alpha(diversities$max, colorlimit = 0.6)

    beta.diversity.min <- plot.beta(diversities$min)
    beta.diversity.max <- plot.beta(diversities$max)

    gs4 <- list(alpha.diversity.min$yaxis,
                alpha.diversity.min$plot,
                beta.diversity.min$plot,
                alpha.diversity.min$legend,
                alpha.diversity.min$xaxis,
                beta.diversity.min$xaxis,
                beta.diversity.min$xlab,
                text_grob("A.", size = 18),
                alpha.diversity.max$yaxis,
                alpha.diversity.max$plot,
                beta.diversity.max$plot,  
                alpha.diversity.max$xaxis,
                beta.diversity.max$xaxis,
                beta.diversity.max$xlab,
                text_grob("B.", size = 18))

    g4 <- arrangeGrob(grobs = gs4,
                      layout_matrix = rbind(
                          c(8,    NA,    NA, NA,   NA, NA, NA),
                          c(NA, 1,    2,    NA, 3, NA, NA),
                          c(NA, 1,    2,    NA, 3, NA, 4),
                          c(NA, NA, 5,    NA,6, NA, NA),
                          c(NA, NA, NA, NA,7, NA, NA),
                          c(15,    NA,    NA, NA,   NA, NA, NA),
                          c(NA, 9,    10,  NA,  11, NA, NA),
                          c(NA, 9,    10,  NA,  11, NA, NA),
                          c(NA, NA, 12,   NA, 13, NA, NA),
                          c(NA, NA, NA, NA,14, NA, NA)),
                      widths=c(0.7, 4, 0.7, 0.1, 5, 0.7, 3),
                      heights=rep(c(1, 1, 6, 1, 2), 2))

    ggsave(file = paste0("cache/alpha-beta-", key , ".png"), plot=g4, height=6, width=9)
    plotlist[[key]] = g4
}
```

@@

alphadiversity <- readRDS("rds-comparepseqs/alpha-R16S.rds")
alphadiversity
